SPARQL on the Open, Decentralised Web

### 2016-06-21 dissertation/introdefhistory.tex
Capitalisation; thanks Helen
detail challenges to validity

\section{Semantic Web -- A definition?}\label{sec:nodef}

@@

\section{Objectivity of the study}\label{sec:objectivity}

@@

The problems are also discussed throughout
\cite{chalmers1999whatis}. It is interesting to consider the example
on page 25, where the author describes a method forwarded by Galileo
Galilei to measure the diameter of a star. The method was objective in
the sense if followed, it would yield the same value today as it did
when Galileo employed it. However, it relied on faulty assumptions and
is therefore invalid. The same kind of problem may occur in the
evaluation of e.g. SPARQL engines. If a benchmark relies on a faulty
workload, the application of the benchmark may seem objective to the
investigator, but its external validity should be
challenged. Moreover, if the benchmark relied on a use case supplied
by e.g. an industrial partner, the validity could be further
challenged based on e.g. the restriction on viewpoint that this
represents.

@@

\section{A personal history}\label{sec:history}

>>>>

\section{Semantic Web -- A Definition?}\label{sec:nodef}

@@

\section{Objectivity of the Study}\label{sec:objectivity}

@@

The problems are also discussed throughout
\cite{chalmers1999whatis}. It is interesting to consider the example
on page 25, where the author describes a method forwarded by Galileo
Galilei to measure the diameter of a star. The method was objective in
the sense if followed, it would yield the same value today as it did
when Galileo employed it. However, it relied on faulty assumptions and
is therefore invalid. The same kind of problem may occur in the
evaluation of e.g. SPARQL engines. If a benchmark relies on a faulty
workload, the application of the benchmark may seem objective to the
investigator, but its external validity should obviously be
challenged. Moreover, if the benchmark relied on a use case supplied
by e.g. an industrial partner, the validity could be further
challenged based on e.g. the restriction on viewpoint that this
represents. However, such challenges are scarcely seen in the literature.

@@

\section{A Personal History}\label{sec:history}
